Performance-portable Parallel Programming in Computer Science Education with Kokkos

### 2020-01-24 src/2.GenericProgramming.tex
Minor changes.

\emph{Constrained semantics} provided by the programmer to the parallel programming model can be grouped into information to express intent or correctness and properties that control critical performance aspects. They address the question of \emph{what}, \emph{where} and \emph{how}. In the context of parallel programming, these correspond to defining which code portion to parallelize, where to run the code, where to access the data, and how to run that parallel code. Synchronization primitives may be considered part of the ``what,'' and information on the execution properties such as data placement or memory access type may be considered as part of the ``how.'' Application logic is expressed following a \emph{paradigm} implemented in a \emph{programming language}.

@@

Lastly, a language defines the syntax of the parallel semantic. Annotations-based  languages add semantic information to the base language through pragmas while embedded programming models rely on the base language and offer additional programming interfaces to capture information. Their semantic is defined in the API specification.

>>>>

\emph{Constrained semantics} provided by the programmer to the parallel programming model can be grouped into information to express intent or correctness and properties that control critical performance aspects. They address the question of \emph{what}, \emph{where} and \emph{how}. In the context of parallel programming, these correspond to defining which code portion to parallelize, where to run the code, where to access the data, and how to run that parallel code. Synchronization primitives may be considered part of the \emph{what}, and information on the execution properties such as data placement or memory access type may be considered as part of the \emph{how}. Application logic is expressed following a \emph{paradigm} implemented in a \emph{programming language}.

@@

A language defines the syntax of the parallel semantic. Annotations-based  languages add semantic information to the base language through pragmas while embedded programming models rely on the base language and offer additional programming interfaces to capture information. Their semantic is defined in the API specification.
